A parallel general purpose multi-objective optimization framework, with application to electron beam dynamics

### 2019-03-21 paper/submission/prab.tex
finishing response 2

The next section introduces the notation of multi-objective optimization
theory and describes the first implemented optimizer.
In Section~\ref{sec:framework}, the implementation of the framework is discussed.
We introduce the employed forward-solver in Section~\ref{sec:forward-solver}.
A validation and a proof of concept application in the beam dynamics problems 
mentioned above is discussed in Section~\ref{sec:experiments}.

@@

Simulation based multi-objective optimization problems are omnipresent in
  research and industry.
These simulation and optimization problems are in
  general very big and computationally demanding.
This motivated us to design a massively parallel general purpose framework.
The key traits of such a design can be summarized as:
%
\begin{itemize}
  \item support any multi-objective optimization method,
  \item support any function evaluator: simulation code or measurements,
  \item offer a general description/specification of objectives, constraints
        and design variables,
  \item run efficiently in parallel on current large-scale high-end clusters
        and supercomputers.
\end{itemize}
%

@@

The framework presented in \cite{lems:09} resembles our implementation the
  most, aside from their tight coupling with an evolutionary algorithm
  optimization strategy.
The authors propose a plug-in based framework employing an island
  parallelization model, where multiple populations are evaluated concurrently
  and independently up to a point where some number of individuals of the
  population are exchanged.
This is especially useful to prevent the search algorithm getting stuck in
  a local minimum.
A set of default plug-ins for genetic operators, selectors and other
  components of the algorithms are provided by their framework.
User-based plug-ins can be incorporated into the framework by implementing a
  simple set of functions.

>>>>

The next section introduces the notation of multi-objective optimization
theory and describes the first implemented optimizer.
A validation and a proof of concept application in the beam dynamics problems 
mentioned above is discussed in Section~\ref{sec:experiments}.
The implementation of the framework and forward-solver is 
discussed in Supplemental Material at [URL will be inserted by publisher].

@@

Simulation based multi-objective optimization problems are omnipresent in
  research and industry.
These simulation and optimization problems are in
  general very big and computationally demanding.
This motivated us to design a massively parallel general purpose framework.
The key traits of such a design can be summarized as:
%
\begin{itemize}
  \item support any multi-objective optimization method,
  \item support any function evaluator: simulation code or measurements,
  \item offer a general description/specification of objectives, constraints
        and design variables,
  \item run efficiently in parallel on current large-scale high-end clusters
        and supercomputers.
\end{itemize}

@@

The framework presented in~\cite{lems:09} resembles our implementation the
  most, aside from their tight coupling with an evolutionary algorithm
  optimization strategy.
The authors propose a plug-in based framework employing an island
  parallelization model, where multiple populations are evaluated concurrently
  and independently up to a point where some number of individuals of the
  population are exchanged.
This is especially useful to prevent the search algorithm getting stuck in
  a local minimum.
A set of default plug-ins for genetic operators, selectors and other
  components of the algorithms are provided by their framework.
User-based plug-ins can be incorporated into the framework by implementing a
  simple set of functions (See Supplemental Material).

### 2019-03-21 paper/submission/supplemental_material.tex
finishing response 2

The basic assumption in simulation-based optimization is that a
  call to an expensive simulation software component present in the
  constraints or objectives is needed.
The framework is divided in three exchangeable components, as shown in
  Fig.~\ref{fig:opt-framework-layout}, to encapsulate the major behavioral
  patterns of the framework.
%
\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{opt-framework-layout}
  \caption{Schematic view of messages passed within the network between the
    three roles.
  The dashed cyan path describes a request (job $j_1$) sent from $O_i$ to the
  \textsc{Pilot} being handled by $W_j$. Subsequently the result $r_1$ is
  returned to the requesting \textsc{Optimizer} ($O_i$). $W_j$ are beam dynamics 
  simulations within OPAL.}
  \label{fig:opt-framework-layout}
\end{figure}

%
The \textsc{Pilot} component acts as a bridge between the optimizer and
  forward solvers, providing the necessary functionality to handle passing
  requests and results between the \textsc{Optimizer} and the
  \textsc{Simulation} modules.
The framework was implemented in \texttt{C++}, utilizing features like template
parameters to specify the composition of the framework.
``Default'' implementations are provided that can be controlled via command line options.
Due to its modular design, all components can be completely customized.

Every available MPI process will take up one of the three available roles (see
  Fig.~\ref{fig:framenetwork}):  one process acts as \textsc{Pilot}, the
  remaining processes are divided amongst \textsc{Worker} and
  \textsc{Optimizer} roles.
Both, the \textsc{Worker} and the \textsc{Optimizer} can consist of multiple
  MPI processes to exploit parallelism.
As shown in Fig.~\ref{fig:opt-framework-layout}, the \textsc{Pilot} is used
  to coordinate all ``information requests'' between the \textsc{Optimizer}
  and the \textsc{Worker}.
An information request is a job that consists of a set of design variables
  (e.g.~the genes of an individual) and a type of information it requests
  (e.g.~function evaluation or derivative).
The \textsc{Pilot} keeps checking for idle \textsc{Worker}s and assigns jobs
  in the queue to any free \textsc{Worker}.
Once the \textsc{Worker} has computed and evaluated the request its results
  are returned to the \textsc{Optimizer} that originally requested the
  information.

@@

If the objectives and constraints are simple arithmetical expressions, 
the \texttt{FunctionEvaluator} simulator can be used.
Using functors and the default expression primitives, 
multi-objective optimization problems can be specified, 
i.e.\ the benchmark problem presented in \cite{hbwh:05}:
%

	\begin{widetext}
		\begin{align} \label{eqn:bench}
		\text{min} & \left[ 1 - \exp \left( -1 \left(
		\left(x_1 - \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_2 - \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_3 - \frac{1}{\sqrt{3}} \right)^2 \right)\right), \right. \\
		\vspace{3em} 
		& \left. 1 - \exp \left( -1 \left(
		\left(x_1 + \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_2 + \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_3 + \frac{1}{\sqrt{3}} \right)^2 \right)\right) \right]^T \nonumber \\
		\vspace{3em} \nonumber \\
		\text{s.t.} \quad & \quad -1 \le x_i \le 1, \quad i=1,2,3 \nonumber
		\text{.} \nonumber
		\end{align}
	\end{widetext}

@@

This examples serves to show how a user can 
set up a multiobjective optimization run 
within an OPAL input file.

The code that follows was used to perfrom ex-1 in Section~\ref{sec:experiments}.

>>>>

The basic assumption in simulation-based optimization is that a
  call to an expensive simulation software component present in the
  constraints or objectives is needed.
The framework is divided in three exchangeable components, as shown in
  Fig.~\ref{fig:opt-framework-layout}, to encapsulate the major behavioral
  patterns of the framework.
%
\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{opt-framework-layout}
  \caption{Schematic view of messages passed within the network between the
    three roles.
  The dashed cyan path describes a request (job $j_1$) sent from $O_i$ to the
  \textsc{Pilot} being handled by $W_j$. Subsequently the result $r_1$ is
  returned to the requesting \textsc{Optimizer} ($O_i$). $W_j$ are beam dynamics 
  simulations within OPAL.}
  \label{fig:opt-framework-layout}
\end{figure}
%
The \textsc{Pilot} component acts as a bridge between the optimizer and
  forward solvers, providing the necessary functionality to handle passing
  requests and results between the \textsc{Optimizer} and the
  \textsc{Simulation} modules.
The framework was implemented in \texttt{C++}, utilizing features like template
parameters to specify the composition of the framework.
``Default'' implementations are provided that can be controlled via command line options.
Due to its modular design, all components can be completely customized.

Every available MPI process will take up one of the three available roles (see
  Fig.~\ref{fig:framenetwork}):  one process acts as \textsc{Pilot}, the
  remaining processes are divided amongst \textsc{Worker} and
  \textsc{Optimizer} roles.
Both, the \textsc{Worker} and the \textsc{Optimizer} can consist of multiple
  MPI processes to exploit parallelism.
As shown in Fig.~\ref{fig:opt-framework-layout}, the \textsc{Pilot} is used
  to coordinate all ``information requests'' between the \textsc{Optimizer}
  and the \textsc{Worker}.
An information request is a job that consists of a set of design variables
  (e.g.~the genes of an individual) and a type of information it requests
  (e.g.~function evaluation or derivative).
The \textsc{Pilot} keeps checking for idle \textsc{Worker}s and assigns jobs
  in the queue to any free \textsc{Worker}.
Once the \textsc{Worker} has computed and evaluated the request its results
  are returned to the \textsc{Optimizer} that originally requested the
  information.
%
\begin{figure}%[h!]
	\center
	\includegraphics[width=0.5\textwidth]{opt-framework_code}
	\caption{Multi-objective framework: the pilot (master) solves the
		optimization problem specified in the input file by coordinating optimizer
		algorithms and workers running forward solves.}
	\label{fig:framenetwork}
\end{figure}

@@

If the objectives and constraints are simple arithmetical expressions, 
the \texttt{FunctionEvaluator} simulator can be used.
Using functors and the default expression primitives, 
multi-objective optimization problems can be specified, 
such as the benchmark problem presented in~\cite{hbwh:05}, 
which was used for validation in Section IV, subsection A of the paper.

@@

This examples serves to show how a user can 
set up a multiobjective optimization run 
within an OPAL input file. 
The code that follows was used to perform ex-1 in 
Section IV, subsection B of the paper. 
The template file referenced as \verb|optLinac_40nC.tmpl| contained the 
element definitions for the AWA beam line.

\begin{verbatim}
	OPTION, ECHO=FALSE;
	OPTION, INFO=TRUE;

	TITLE, STRING="ANL Optimisation";

	dv0: DVAR, VARIABLE="IBF",    LOWERBOUND=200.0, UPPERBOUND=500.0;
	dv1: DVAR, VARIABLE="IM",     LOWERBOUND=170.0, UPPERBOUND=260.0;
	dv2: DVAR, VARIABLE="GPHASE", LOWERBOUND=-30.0, UPPERBOUND=0.0;
	dv3: DVAR, VARIABLE="FWHM",   LOWERBOUND=1.5,   UPPERBOUND=10.0;

	// Quad values
	dv4: DVAR, VARIABLE="KQ1", LOWERBOUND=-8.0, UPPERBOUND=8.0;
	dv5: DVAR, VARIABLE="KQ2", LOWERBOUND=-8.0, UPPERBOUND=8.0;
	dv6: DVAR, VARIABLE="KQ3", LOWERBOUND=-8.0, UPPERBOUND=8.0;
	dv7: DVAR, VARIABLE="KQ4", LOWERBOUND=-8.0, UPPERBOUND=8.0;

	rmss1:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',16.5))";
	emitx1: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',16.5))";
	rmss2:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',18.5))";
	emitx2: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',18.5))";
	c1: CONSTRAINT, EXPR="fabs(statVariableAt('rms_x',16.5))<1.0e-1";
	c2: CONSTRAINT, EXPR="fabs(statVariableAt('rms_y',16.5))<1.0e-1";

	OPTIMIZE, INPUT="tmpl/optLinac_40nC.tmpl",
	OUTPUT="optLinac_40nC",
	OUTDIR="results",
	OBJECTIVES = {rmss1, emitx1, rmss2, emitx2},
	DVARS = {dv0, dv1, dv2, dv3, dv4, dv5, dv6, dv7},
	CONSTRAINTS = {c1, c2},
	INITIALPOPULATION=80,
	MAXGENERATIONS=100,
	NUM_MASTERS=1,
	NUM_COWORKERS=8,
	SIMTMPDIR="tmp",
	TEMPLATEDIR="tmpl",
	FIELDMAPDIR="fieldmaps",
	NUM_IND_GEN=80,
	GENE_MUTATION_PROBABILITY=0.1,
	MUTATION_PROBABILITY=0.1,
	RECOMBINATION_PROBABILITY=0.9;
	QUIT;
\end{verbatim}

### 2019-03-21 paper/submission/theor-experiment.tex
finishing response 2

\subsection{Optimizer Validation}

\begin{figure}
    \centering
      \includegraphics[width=0.4\linewidth]{hypervolume}
  \caption{The hypervolume for a two-objective optimization problem
  corresponds to the shaded area formed by the dashed rectangles spanned by
  all points on the Pareto front and an arbitrary selected origin $p_o$.}
  \label{fig:hypervolume}
\end{figure}

To ensure that the optimizer works correctly, the benchmark
  problem (\ref{eqn:bench}) was solved.
To that end, we use a metric for comparing the quality of a Pareto front.
Given a point in the Pareto set, we compute the $m$ dimensional volume (for
  $m$ objectives) of the dominated space, relative to a chosen origin.
This is visualized for $2$ objectives in Fig.~\ref{fig:hypervolume}.
For further information and details of the implementation see~\cite{whbb:12}.
Figure~\ref{fig:pisa_bench} and the corresponding hypervolume values in
  Table~\ref{tbl:bench_rms_error} show expected convergence.
The reference Pareto front is clearly very well approximated.
It took a total of 1100 function evaluations to perform this computation.
The hypervolume of the reference solution ($0.6575$) for our benchmark was
 computed by sampling the solution provided in~\cite{hbwh:05}.
\begin{figure}
  \centering
    \includegraphics[width=0.6\linewidth]{valid_front}
  \caption{Variator benchmark after $1100$ function evaluations using binary
           crossover and independent gene mutations (each gene mutates with
           probability $p=\frac{1}{2}$) on a population of $100$
           individuals.}
  \label{fig:pisa_bench}
\end{figure}
\begin{table}%[h!]
\begin{center}
  \caption{Convergence of benchmark problem with errors relative to
    hypervolume of sampled reference solution.}
  \label{tbl:bench_rms_error}
  \begin{tabular}{c|c|c}
	\cline{1-3}
    tot.\ function  & hypervolume & relative error\\
    evaluations    & & \\
	\cline{1-3}
    100  &  0.859753 & $3.076 \times 10^{-1}$ \\
    200  &  0.784943 & $1.938 \times 10^{-1}$ \\
    500  &  0.685183 & $4.210 \times 10^{-2}$ \\
    900  &  0.661898 & $6.689 \times 10^{-3}$ \\
    1100 &  0.657615 & $1.749 \times 10^{-4}$ \\
	\cline{1-3}
  \end{tabular}
\end{center}
\end{table}
Table~\ref{tbl:bench_rms_error} shows satisfactory
  convergence to the sampled reference Pareto front after 1000 (plus the
  additional 100 evaluations for the initial population) function evaluations.

\subsection{AWA Photoinjector Optimization} \label{awaproblem}
Next the optimization framework is applied to the high charge beam line
 at the Argonne Wakefield Accelerator (AWA) facility. 
The goal of this optimization is to produce beams of electrons that meet 
design specifications; this includes number of particles (charge), energy, 
and particle distribution (characterized by beam sizes and energy spread).
As shown in Fig.~\ref{awa-linac}, the installed portion of the the 
beam line consists of an rf photocathode gun, 
two solenoids, and six linear accelerating cavities
followed by four quadrupoles and a stripline kicker. 
The charge of interest, 40 nC, is needed for two beam acceleration (TBA) 
experiments performed at the AWA~\cite{gai_power_jing_2012,JING201872}, 
which motivates this work. 
Prior experimental results were limited by beam size when the beam passed through small aperture 
wakefield structures located downstream. 
In an attempt to maximize charge transmission in upcoming experiments,
magnet strengths of the solenoids and quadrupoles leading into the 
TBA section of the beam line were optimized, shown in Fig.~\ref{awa-tba}.
The simulation model includes from the gun to the septum.
The optimization location is chosen as the  
entrance to the first quadrupole on the dog leg ($s_3$), see Fig.~\ref{awa-tba}.
Minimizing beam sizes here will enable capture and further focusing before space charge effects dominate the beam. 
This will also enable cleaner transport through downstream elements.
%\vspace{-1em}

@@

\subsubsection{Hyper parameter Scan}
While the optimization problem and goals were well defined (Subsection \ref{awaproblem}), 
it was not clear what the best hyper parameters for the genetic algorithm would be.
These parameters include gene mutation probability, mutation probability, 
recombination probability, number of individuals, 
and number of generations to complete. 
Given the beam line in Fig.~\ref{awa-linac},
four small optimization experiments were done with various hyper parameters. 
Similar to the time step scan, 
the goal of this exercise was to determine which set of optimization
parameters strongly influence the results, 
and whether there was a time to solution difference.
From here on, we will reference each experiment as ex-1, ex-2, ex-3, and ex-4
as shown in Table \ref{extable}. 
\begin{table}%[h!]
\begin{center}
\caption{Input Parameters for initial twenty-four hour AWA optimization experiments. 
The gene mutation probability was equal to the mutation probability (not shown) in all four experiments. 
The max number of individuals per generation was~80.}
\label{extable}
\begin{tabular}{c|c|c|c}
\cline{1-4}
& Gene Mutation \qquad& Recombination \qquad & Number of completed \vspace{-0.75em}\\
Experiment & Probability & Probability &  generations \\ 
\cline{1-4}
ex-1 &  0.1  & 0.9  &  96 \\
ex-2 &  0.3  & 0.7  &  81 \\
ex-3 &  0.8  & 0.2  &  53 \\
ex-4 &  0.01 & 0.09 &  95 \\ 
\cline{1-4}
\end{tabular}
\end{center}
\end{table}

The maximum number of individuals per generation was fixed at 80. 
This number was chosen based on the node architecture, and  
to prevent a prohibitive computational cost.  
Each experiment was allowed to run for twenty-four hours, with 
a maximum generation limit of 100. 
We reduced the six objectives to four, 
and shortened the simulation time by moving the objectives further 
upstream to $s_1$ and $s_2$, the locations before and after the kicker, 
see Fig.~\ref{awa-tba}.  
The objectives include: $\varepsilon_{x}\left(s = s_1\right)\text{, } \varepsilon_{x}\left(s = s_2\right)$, $\text{rms}_{s}\left(s = s_1\right)\text{, and }  \text{rms}_{s}\left(s = s_2\right)$. 
An example OPAL input file, used to perform the optimization in ex-1, 
can be found in Supplemental Material at [URL will be inserted by publisher].
All other optimization runs in the paper use this input file format.

@@

\begin{figure}
	\includegraphics[width=0.65\textwidth]{xy-max-min-sigma-paper}
	\caption{Optimized beam sizes along high charge beam line. The gun is located at $s=0$, 
	both x and y beam sizes are shown. The black line represents the relevant beam line aperture, while
	the green line indicates the location of the optimization.}
	\label{fig:stat}
\end{figure}
\begin{table}%[h!]
	\begin{center}
		\caption{Input Parameters for the optimized solution shown in Figures~\ref{fig:pareto1} and \ref{fig:stat}.}
		\label{tab:designopt}   
		\begin{tabular}{l|c|c}
			\cline{1-3}
			\textbf{Design Variable} \qquad \qquad & \textbf{Unit}	\quad&  \textbf{Value}  \\ 
			\cline{1-3}
			{Buck Focusing Solenoid} \qquad \qquad & amps	\quad & 478 \\
			Matching Solenoid &	amps	& 197	  \\
			Quadrupole 1& T-m		& -0.8	\\ 
			Quadrupole 2& T-m		& 0.9	\\
			Quadrupole 3 & T-m		& 0.8	\\
			Quadrupole 4 & T-m		& -1.0	\\ 
			Bunch Length & mm 		& 1.5	\\
			\cline{1-3}
		\end{tabular}
	\end{center}
\end{table}

>>>>

\subsection{Optimizer Validation}
To ensure that the optimizer works correctly, the benchmark problem presented in~\cite{hbwh:05}, 
  \begin{widetext}
  	\begin{align} \label{eqn:bench}
  	\text{min} & \left[ 1 - \exp \left( -1 \left(
  	\left(x_1 - \frac{1}{\sqrt{3}} \right)^2 +
  	\left(x_2 - \frac{1}{\sqrt{3}} \right)^2 +
  	\left(x_3 - \frac{1}{\sqrt{3}} \right)^2 \right)\right), \right. \\
  	\vspace{3em} 
  	& \left. 1 - \exp \left( -1 \left(
  	\left(x_1 + \frac{1}{\sqrt{3}} \right)^2 +
  	\left(x_2 + \frac{1}{\sqrt{3}} \right)^2 +
  	\left(x_3 + \frac{1}{\sqrt{3}} \right)^2 \right)\right) \right]^T \nonumber \\
  	\vspace{3em} \nonumber \\
  	\text{s.t.} \quad & \quad -1 \le x_i \le 1, \quad i=1,2,3 \nonumber
  	\text{.} \nonumber
  	\end{align}
  \end{widetext}
was solved with the framework.  
To that end, we use a metric for comparing the quality of a Pareto front.
Given a point in the Pareto set, we compute the $m$ dimensional volume (for
  $m$ objectives) of the dominated space, relative to a chosen origin.
This is visualized for $2$ objectives in Fig.~\ref{fig:hypervolume}.
For further information and details of the implementation see~\cite{whbb:12}.
Figure~\ref{fig:pisa_bench}, and the corresponding hypervolume values in
Table~\ref{tbl:bench_rms_error}, show expected convergence.
The reference Pareto front is well approximated.
It took a total of 1100 function evaluations to perform this computation.
The hypervolume of the reference solution ($0.6575$) for our benchmark was
 computed by sampling the solution provided in~\cite{hbwh:05}.
 Table~\ref{tbl:bench_rms_error} shows satisfactory
 convergence to the sampled reference Pareto front after 1000 (plus the
 additional 100 evaluations for the initial population) function evaluations.
 \begin{figure}
 	\centering
 	\includegraphics[width=0.4\linewidth]{hypervolume}
 	\caption{The hypervolume for a two-objective optimization problem
 		corresponds to the shaded area formed by the dashed rectangles spanned by
 		all points on the Pareto front and an arbitrary selected origin $p_o$.}
 	\label{fig:hypervolume}
 \end{figure}
\begin{figure}
  \centering
    \includegraphics[width=0.6\linewidth]{valid_front}
  \caption{Variator benchmark after $1100$ function evaluations using binary
           crossover and independent gene mutations (each gene mutates with
           probability $p=\frac{1}{2}$) on a population of $100$
           individuals.}
  \label{fig:pisa_bench}
\end{figure}
\begin{table}%[h!]
\begin{center}
  \caption{Convergence of benchmark problem with errors relative to
    hypervolume of sampled reference solution.}
  \label{tbl:bench_rms_error}
  \begin{tabular}{c|c|c}
	\cline{1-3}
    tot.\ function  & hypervolume & relative error\\
    evaluations    & & \\
	\cline{1-3}
    100  &  0.859753 & $3.076 \times 10^{-1}$ \\
    200  &  0.784943 & $1.938 \times 10^{-1}$ \\
    500  &  0.685183 & $4.210 \times 10^{-2}$ \\
    900  &  0.661898 & $6.689 \times 10^{-3}$ \\
    1100 &  0.657615 & $1.749 \times 10^{-4}$ \\
	\cline{1-3}
  \end{tabular}
\end{center}
\end{table}

\subsection{AWA Photoinjector Optimization} \label{awaproblem}
Next the optimization framework is applied to the high charge beam line
 at the Argonne Wakefield Accelerator (AWA) facility. 
The goal of this optimization is to produce beams of electrons that meet 
design specifications; this includes number of particles (charge), energy, 
and particle distribution (characterized by beam sizes and energy spread).
As shown in Fig.~\ref{awa-linac}, the installed portion of the the 
beam line consists of an rf photocathode gun, 
two solenoids, and six linear accelerating cavities
followed by four quadrupoles and a stripline kicker. 
The charge of interest, \SI{40}{nC}, is needed for two beam acceleration (TBA) 
experiments performed at the AWA~\cite{gai_power_jing_2012,JING201872}, 
which motivates this work. 
Prior experimental results were limited by beam size when the beam passed through small aperture 
wakefield structures located downstream. 
In an attempt to maximize charge transmission in upcoming experiments,
magnet strengths of the solenoids and quadrupoles leading into the 
TBA section of the beam line were optimized, shown in Fig.~\ref{awa-tba}.
The simulation model includes from the gun to the septum.
The optimization location is chosen as the  
entrance to the first quadrupole on the dog leg ($s_3$), see Fig.~\ref{awa-tba}.
Minimizing beam sizes here will enable capture and further focusing before space charge effects dominate the beam. 
This will also enable cleaner transport through downstream elements.
%\vspace{-1em}

@@

\subsubsection{Hyper parameter Scan}
While the optimization problem and goals were well defined (Subsection \ref{awaproblem}), 
it was not clear what the best hyper parameters for the genetic algorithm would be.
These parameters include gene mutation probability, mutation probability, 
recombination probability, number of individuals, 
and number of generations to complete. 
Given the beam line in Fig.~\ref{awa-linac},
four small optimization experiments were done with various hyper parameters. 
Similar to the time step scan, 
the goal of this exercise was to determine which set of optimization
parameters strongly influence the results, 
and whether there was a time to solution difference.
From here on, we will reference each experiment as ex-1, ex-2, ex-3, and ex-4
as shown in Table \ref{extable}. 
\begin{table}%[h!]
\begin{center}
\caption{Input Parameters for initial twenty-four hour AWA optimization experiments. 
The gene mutation probability was equal to the mutation probability (not shown) in all four experiments. 
The max number of individuals per generation was~80.}
\vspace{1em}
\label{extable}
\begin{tabular}{c|c|c|c}
\cline{1-4}
& Gene Mutation \qquad& Recombination \qquad & Number of completed \vspace{-0.75em}\\
Experiment & Probability & Probability &  generations \\ 
\cline{1-4}
ex-1 &  0.1  & 0.9  &  96 \\
ex-2 &  0.3  & 0.7  &  81 \\
ex-3 &  0.8  & 0.2  &  53 \\
ex-4 &  0.01 & 0.09 &  95 \\ 
\cline{1-4}
\end{tabular}
\end{center}
\end{table}

The maximum number of individuals per generation was fixed at 80. 
This number was chosen based on the node architecture, and  
to prevent a prohibitive computational cost.  
Each experiment was allowed to run for twenty-four hours, with 
a maximum generation limit of 100. 
We reduced the six objectives to four, 
and shortened the simulation time by moving the objectives further 
upstream to $s_1$ and $s_2$, the locations before and after the kicker, 
see Fig.~\ref{awa-tba}.  
The objectives include: $\varepsilon_{x}\left(s = s_1\right)\text{, } \varepsilon_{x}\left(s = s_2\right)$, $\text{rms}_{s}\left(s = s_1\right)\text{, and }  \text{rms}_{s}\left(s = s_2\right)$. 
An example OPAL input file, used to perform the optimization in ex-1, 
can be found in Supplemental Material at [URL will be inserted by publisher].
All other optimization runs in the paper follow this template.

@@

\begin{figure}
	\includegraphics[width=0.65\textwidth]{xy-max-min-sigma-paper}
	\caption{Optimized beam sizes along high charge beam line. The gun is located at $s=0$, 
	both x and y beam sizes are shown. The black line represents the relevant beam line aperture, while
	the green line indicates the location of the optimization.}
	\label{fig:stat}
\end{figure}
\begin{table}%[h!]
	\begin{center}
		\caption{Input Parameters for the optimized solution shown in Figures~\ref{fig:pareto1} and \ref{fig:stat}.}
		\label{tab:designopt}  
		\vspace{1em} 
		\begin{tabular}{l|c|c}
			\cline{1-3}
			\textbf{Design Variable} \qquad \qquad & \textbf{Unit}	\quad&  \textbf{Value}  \\ 
			\cline{1-3}
			{Buck Focusing Solenoid} \qquad \qquad & amps	\quad & 478 \\
			Matching Solenoid &	amps	& 197	  \\
			Quadrupole 1& T-m		& -0.8	\\ 
			Quadrupole 2& T-m		& 0.9	\\
			Quadrupole 3 & T-m		& 0.8	\\
			Quadrupole 4 & T-m		& -1.0	\\ 
			Bunch Length & mm 		& 1.5	\\
			\cline{1-3}
		\end{tabular}
	\end{center}
\end{table}
